\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-26 docs/paper/paper.tex

\usepackage{color,soul}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}  
\begin{document}

@@

\begin{abstract}
Our aim is to propose a deep learning approach that surpasses simulations conducted using Full-Vectorial Finite Element Method (FV-FEM) used to design, optimise and evaluate a unique multi-channel Photonic Crystal Fiber (PCF) sensor based on Surface Plasmon Resonance (SPR) structure performance, proposed in our recent work. Through these simulation techniques one must calculate the confinement loss for a specific wavelength and a particular set of geometric properties of the PCF sensor, then repeat the process for different analytes. To eventually find the best set of geometric properties that maximises the distance between the confinement loss distributions of different analytes, and thus find the most sensible PCF sensor. In order to find these distributions we have to make as much calculations per wavelength as possible to ensure the correct location of the peak value of the confinement loss. Simulation methods are not only time costing and daunting, consuming hours to days, but also inaccurate sometimes. In contrast, a deep neural network model astonishingly performs these calculations in milliseconds to seconds, quiet accurately, when it is well trained with an accurate data set.

@@

@@

\begin{figure}[h]
	\hspace*{-0.07\textwidth}
	\begin{subfigure}{.5\textwidth}
    \begin{tikzpicture}
		\begin{axis}[
		xlabel=$Epochs$, 
		ylabel=$Training \space MSE$,
		title={Training MSE of the ANN model},
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=1.1\linewidth,
		no marks]
		\addplot[line width=1pt,solid,color=blue] %
		table{tr_loss_ann.txt};
		\end{axis}
	\end{tikzpicture}
	\end{subfigure}\hspace{0.1\textwidth}
	\begin{subfigure}{.5\textwidth}
	\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 0},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_336.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
	\end{subfigure}
	\caption{}
\end{figure}\\

@@

\begin{table}[h]
\centering
\scalebox{1.2}{\begin{tabular}{l|l}
      & Time elapsed & \\
      \hline
    ANN &  0.17 sec & \\
    \hline
    Simulation &  7872 sec = 2.18 hours  & \\
\end{tabular}
}
\caption{ANN vs Simulation test runtime performance}
\end{table}
\newpage

>>>>

\usepackage{color,soul}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}

\begin{document}

@@

\begin{abstract}
Photonic crystal fibers (PCF) for specific applications are designed and optimized by both industry experts and researches. However, the potential number of combinations possible for a single application is very large. This issue combined by the speed of the commonly used Full Vectorial Finite Element Method (FV-FEM) causes the task to take significant amount of time. As stated in the previous works, artificial neural networks (ANN) can predict the result of numerical simulations much faster. However, there are two issues with the methods proposed previously. Namely, the required number of samples for training and generality of the designed network. In this paper, we  propose the use of generative adversarial networks (GAN) to augment the real data set to train a ANN model. Experimental analysis suggest that the proposed combination not only accurately predicts the confinement loss even with limited amount of data, but also can work in wider range of methods and geometric configurations. Finally, the proposed method is shown to predict the confinement loss over a range of analytes and wavelengths in a completely new set of geometric configuration.

@@

In this section details of the proposed method is discussed. At the start, a GAN is trained to generate additional data by using training samples. These generated samples are filtered to ensure they fall within the applicable range. Original training samples and remaining samples are joined to train a fully-connected feed-forward multi layer perceptron neural network network. The details of the proposed ANN architecture and the GAN is discussed in the following subsections.

\hl{will be split into the subsections.} We will first train ANN model to predict the confinement loss of a SPR based PCF using the original data set collected. Then we will augment the original training data set with generated samples by the GAN, to improve the performance of the ANN model.
Previous works [ref, ref], demonstrated that random data augmentation actually had weakened the performance of the model. Hence, active researches are ongoing to find ways to optimally sample the generated data [ref], in other words to filter out the "good" generated data after training the GAN. In this paper, we will use a simple if-statement to discard values that fall out of our desired ranges for both the independent variables($n_{analyte}, \lambda, \Lambda, d1, d2, d3$), and the confinement loss. In the following sub-sections we discuss the networks architectures.

\subsection{Artificial neural network design}
\label{ssec:ann}
The ANN model employed in this research is a fully-connected feed-forward MLP (Multi Layer Perceptron) consisting of an input layer, an output layer, and 5 hidden layers. Each hidden layer consists of 50 neurons and uses Rectified Linear Unit (ReLU) activation function.

Adam [ref] as the optimizer and the mean squared error as the loss/cost function. To reduce overfitting we use the Early stopping method [reference], that is by saving checkpoints where the best validation mean squared error occurred as we iterate. To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm was used [ref].

@@

\begin{figure}[h]
	\hspace*{-0.07\textwidth}
	\begin{subfigure}{.5\textwidth}
    \begin{tikzpicture}
		\begin{axis}[
		xlabel=$Epochs$, 
		ylabel=$Training \space MSE$,
		title={Training MSE of the ANN model},
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=1.1\linewidth,
		no marks]
		\addplot[line width=1pt,solid,color=blue] %
		table{tr_loss_ann.txt};
		\end{axis}
	\end{tikzpicture}
	\end{subfigure}\hspace{0.1\textwidth}
	\begin{subfigure}{.5\textwidth}
	\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 0},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_336.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
	\end{subfigure}
	\caption{}
\end{figure}

@@

\begin{table}[h]
\centering
\begin{tabular}{l|l}
      & Time elapsed \\
      \hline
    ANN &  0.17 sec \\
    \hline
    Simulation &  7872 sec = 2.18 hours  \\
\end{tabular}

\caption{ANN vs Simulation test runtime performance}
\end{table}
\newpage
